### 2016-09-19 Thesis/DCG_sb-wi-thesis-template/intro/UPS.tex
edits to intro first page

*These authors contributed equally to this work.

This chapter has expanded sections on the proteasomes role in plant biology, proteasome assembly, and proteasome isotypes.

>>>>

\noindent
*These authors contributed equally to the \textit{Methods Mol. Biol.} work.

\noindent
This chapter has expanded sections on the proteasomes role in plant biology, proteasome assembly, and proteasome isotypes.
